\documentclass[a4paper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
  colorlinks=true,
  urlcolor=blue
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=3pt, topsep=4pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}
\newcommand{\entryspace}{\vspace{5pt}}

\begin{document}

\begin{center}
    {\Huge \textbf{Harsha B}} \\
    \vspace{3pt}
    \textbf{AI \& Full Stack Developer} \\
    Bangalore, Karnataka \textbar{} +91-9900469878 \textbar{}
    \href{mailto:harshab845384@gmail.com}{harshab845384@gmail.com} \\
    \href{https://www.linkedin.com/in/harsha-b-0b1034259/}{linkedin.com/in/harsha-b-0b1034259}
    \textbar{}
    \href{https://github.com/harsha-b-dev}{github.com/harsha-b-dev}
    \textbar{}
    \href{https://harsha-portfolio-lilac.vercel.app/}{Portfolio}
\end{center}

\section*{Professional Summary}
Graduated Information Science and Engineering student and AI \& Full Stack Developer with hands-on experience building AI-powered web applications, REST APIs, dashboards, database systems, and machine learning based products. Skilled in React.js, Python, FastAPI, Flask, Node.js, MongoDB, MySQL, AI integration, and analytics tools. Strong interest in creating scalable, user-centric software systems that solve real-world problems.

\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Frontend:} HTML, CSS, JavaScript, React.js
    \item \textbf{Backend:} Python, FastAPI, Flask, Node.js, Express.js, REST APIs
    \item \textbf{Databases:} MySQL, MongoDB, SQLite, SQL
    \item \textbf{AI/ML \& Data:} Machine Learning, AI Integration, scikit-learn, XGBoost, Pandas, NumPy, Groq API
    \item \textbf{Analytics/Tools:} Power BI, Tableau, Excel, Chart.js, Swagger, Postman, Git, GitHub, Render
\end{itemize}

\section*{Professional Experience}
\textbf{AI Junior Engineer} \hfill Jan 2026 -- May 2026 \\
\textit{BEL (Bharat Electronics Limited) / E2E Rosh IT Solutions India Pvt Ltd}
\begin{itemize}
    \item Built AI-integrated full stack application modules using Python, FastAPI, MySQL, MongoDB, JavaScript, and Groq API.
    \item Developed REST APIs, interactive dashboards, database workflows, and deployment-ready backend features.
    \item Worked with Chart.js, Swagger, Render, and GitHub for API documentation, visualization, deployment, and version control.
    \item Contributed to AI-oriented enterprise project activities inside BEL office with focus on backend systems, data workflows, and AI integration.
\end{itemize}

\entryspace
\textbf{MERN Full Stack with AI Trainee} \hfill 3 months \\
\textit{HSBC Digital Skills for Youth Program \textbar{} Yuva Unstoppable}
\begin{itemize}
    \item Built MERN stack modules using React.js, Node.js, Express.js, MongoDB, JavaScript, REST APIs, and Git/GitHub.
    \item Practiced AI integration workflows and production-style full stack development patterns.
\end{itemize}

\section*{Projects}
\textbf{K-GIS -- Karnataka Geographic Identification System} \hfill Government GIS Project
\begin{itemize}
    \item Worked on a GIS-based land identification and approval support system using Karnataka GIS datasets and APIs.
    \item Contributed to the core land identification module for locating land through latitude/longitude, survey number, and map-based polygon selection.
    \item Enabled land area analysis by identifying district, taluk, rural/urban classification, zone, ward, polygon coordinates, and land distribution across districts.
    \item Helped simplify construction feasibility checks by supporting analysis of forest zones, agricultural land, waterbody zones, mineral layers, and other permission-related land classifications.
    \item \textbf{Tech:} FastAPI, Python, GeoPandas, Shapely, PyProj, OpenLayers, K-GIS datasets/APIs.
\end{itemize}

\entryspace
\textbf{CareerForge -- AI Career Prediction Platform} \hfill
\href{https://careerforge-akvt.onrender.com}{Live} \textbar{}
\href{https://github.com/harsha-b-dev/CareerForge}{GitHub}
\begin{itemize}
    \item Built an AI-based career prediction platform using machine learning models with login/signup and prediction history.
    \item Added admin dashboard, CSV export, PWA support, and Android wrapper support.
    \item \textbf{Tech:} Python, Flask, SQLite, scikit-learn, XGBoost, Pandas, NumPy, HTML, CSS, JavaScript.
\end{itemize}

\entryspace
\textbf{Enterprise AI SQL Assistant} \hfill
\href{https://ai-sql-chatbot.onrender.com}{Live} \textbar{}
\href{https://github.com/harsha-b-dev/ai-sql-chatbot}{GitHub}
\begin{itemize}
    \item Developed an AI-powered natural language SQL assistant for converting user questions into SQL queries.
    \item Implemented AI summaries, MySQL database browsing, charts, and insight generation.
    \item \textbf{Tech:} Python, FastAPI, MySQL, Groq API, JavaScript, Chart.js.
\end{itemize}

\entryspace
\textbf{Food Donor -- Full Stack Food Donation Platform} \hfill
\href{https://food-donor-o9d5.onrender.com}{Live} \textbar{}
\href{https://github.com/harsha-b-dev/Food-Donor}{GitHub}
\begin{itemize}
    \item Built a full stack platform for donating, browsing, accepting, and tracking food donations.
    \item Created admin dashboard and donation management workflows.
    \item \textbf{Tech:} Python, Flask, SQLite, HTML, CSS, Jinja2.
\end{itemize}

\section*{Education}
\textbf{B.E. in Information Science and Engineering} \\
Sri Krishna Institute of Technology, Bangalore \hfill CGPA: 8.0

\vspace{2pt}
\textbf{Pre-University} \\
JS Pre University College, Bangalore \hfill 80\%

\section*{Certifications}
\begin{itemize}
    \item MERN Full Stack with AI -- HSBC
    \item Test Engineer -- Infosys Finishing for Employability Program
    \item Full Stack Development -- Novitech Pvt. Ltd.
    \item Python Basics for Data Science -- EDX
\end{itemize}

\section*{Achievements}
\begin{itemize}
    \item Amazon ML Challenge 2025 -- Team Leader; secured Top 250 rank across India.
    \item Built an ML-based discount and pricing optimization project.
    \item Participated in Build for Bengaluru Hackathon and ANVESHANA 2026 Project Exhibition.
    \item Gained BEL defence sector AI project exposure through enterprise AI project activities.
\end{itemize}

\end{document}
